### 2015-03-18 evaluation.tex
update to table

>>>>

Our experiments used the default \corral context switch bound \texttt{/k:2}. A higher context switch bound would result into deeper interleavings being explored and thus a larger sequentialised program. Intuitively, this means that we would see even greater speedups using information from \whoop, when exploring deeper interleavings. \PDComment{We should take a few measurements with higher k -- no need to be in the table -- just to verify this argument.}
